Supporting Information

### 2018-04-09 SupportingInformation.Rmd
minor change in anolis data calculation

## Phylogenetic data  \label{Phylo_data}
```{r calculation_phylo_data, echo=F, results="hide"}
source("getcopula.R")
phylo_dat<-read.csv("./Data/Anolis/contrasts.csv",header = F)
# Input :
#        data : a dataframe : phylo_dat with dim.=[99 x 14]
#        i, j : column indices of data frame to get bivariate data set, should be (i,j)<=13
#        ploton : logical for option plots of raw data and it's copula representation
# Output : 
#        a cop rank matrix for the raw data
phylo_dat_fn<-function(data,i,j,ploton=T){

>>>>

## Phylogenetic data  \label{Phylo_data}
```{r calculation_phylo_data, echo=F, results="hide"}
source("getcopula.R")
phylo_dat<-read.csv("./Data/Anolis/contrasts.csv",header = T)
# Input :
#        data : a dataframe : phylo_dat with dim.=[99 x 14]
#        i, j : column indices of data frame to get bivariate data set, should be (i,j)<=13
#        ploton : logical for option plots of raw data and it's copula representation
# Output : 
#        a cop rank matrix for the raw data
phylo_dat_fn<-function(data,i,j,ploton=T){
